---
title: "Wind Energy Consumption/Production Trend Analysis and Forecast"
author: "Chuqi Cai, Xueying Feng, Longyi Yang"
fontsize: 12pt
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
  html_document:
    df_print: paged
mainfont: Times New Roman
geometry: margin=2.54cm
subtitle: Time Series Analysis and Forecast
editor_options:
  chunk_output_type: inline
---

\newpage
\tableofcontents 
\newpage
\listoftables 
\newpage
\listoffigures 
\newpage

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Load your packages
library(plyr) #Tools for Splitting, Applying and Combining Data
library(tidyverse) #Getting data frames to tidy
library(lubridate) #For dates and date-times

require(ggplot2)
#install.packages("ggrepel") 
require(ggrepel)

#Load/install required package here
library(forecast)  
library(Kendall)
library(tseries)
#library(outliers)
library(smooth)

library(kableExtra)

# Set your ggplot theme
mytheme <- theme_minimal(base_size = 12, base_family = "Times") + 
  theme(axis.text.x = element_text(color = "DarkGrey"),
        legend.position = "top") 
theme_set(mytheme)
```


# Rationale and Research Questions


\newpage

# Dataset Information

## Database Information
Introduce the source of our Data

## Data Content Information
Introduce the variable we are focusing on. Metadata from https://data.open-power-system-data.org/time_series/




\newpage


# Exploratory Analysis 
-wrangle data: sum up the generation per day. 
-initial plots (clean data if necessary, outliers, missing data)
-decompose

```{r Clean data}
# Load your datasets
Wind_Gen <- read.csv("./Data/DE_Wind_Generation_Data.csv")
str(Wind_Gen)

# Clean time column
Wind_Gen$Time <- as.Date(Wind_Gen$utc_timestamp, format='%Y-%m-%d %H:%M:%OS')
str(Wind_Gen)


Wind_Gen_new <-  Wind_Gen%>%
  group_by(Time=floor_date(Time,unit="week",week_start = 4)) %>%
  summarize(Daily_wind_gen = sum(wind_generation_actual, na.rm = TRUE),
            Daily_offwind_gen = sum(wind_offshore_generation_actual, na.rm = TRUE),
            Daily_onwind_gen = sum(wind_onshore_generation_actual, na.rm = TRUE))

str(Wind_Gen_new)

```


```{r Covert to Time Series}
#Observations start in January 2015 and end in Sep 2020
sample<-Wind_Gen_new[which(Wind_Gen_new$Time>="2015-01-01" & Wind_Gen_new$Time<="2019-12-31"),]
full<-Wind_Gen_new[which(Wind_Gen_new$Time>="2015-01-01" & Wind_Gen_new$Time<="2020-09-30"),]

str(sample)

#Convert to time series
sample_off <- sample[,c(1,3)]
sample_ts<-ts(sample[,2:4], frequency = 52, start = c(2015,1,1), end = c(2020,01,01))
full_ts<-ts(full[,2:4], frequency = 52, start = c(2015,1,1))
sample_off_ts <- sample_ts[,2]

sample_msts <- msts(sample_off$Daily_offwind_gen,
                    seasonal.periods = c(52),
                    start = c(2015,01,01))
```


```{r Plot}
#Plot 
ggplot(sample, aes(x=Time, y=sample$Daily_wind_gen)) +
  geom_line(color="blue") +
  ylab("Wind Generation (MW)") +
  geom_line(aes(y=sample$Daily_offwind_gen, col="Offshore Wind"))+
  geom_line(aes(y=sample$Daily_onwind_gen, col="Onshore wind"))+
  theme(legend.position = "right") +
  scale_x_date(date_breaks = "1 years", date_labels = "%Y")

#Plot offshore
ggplot(sample, aes(x=Time, y=sample$Daily_offwind_gen)) +
  geom_line(color="blue") +
  ylab("Wind Generation (MW)") +
  theme(legend.position = "right") +
  scale_x_date(date_breaks = "1 years", date_labels = "%Y")

#ACF and PACF plots
par(mar=c(3,3,3,0));par(mfrow=c(1,2))
ACF_Plot <- Acf(sample_ts[,3], lag = 100, plot = TRUE,main="ACF of Offshore wind")
PACF_Plot <- Pacf(sample_ts[,3], lag = 100, plot = TRUE,main="PACF of Offshore wind")
```


\newpage

# Analysis

## Anlysis Trends
-trends
```{r}
#Decompose
sample_ts_off_decompose <- decompose(sample_ts[,"Daily_offwind_gen"],
                                 type = "additive")
sample_ts_off_deseason <- seasadj(sample_ts_off_decompose)
sample_msts_mstl <- mstl(sample_msts) 
#plot
plot(sample_ts_off_decompose)
plot(sample_ts_off_deseason)
plot(sample_msts_mstl)
#ACF and PACF
acf(sample_ts_off_deseason)
pacf(sample_ts_off_deseason)

#Mann-Kendall test
print(
  summary(MannKendall(sample_ts_off_deseason))
)
#The P-value is less than 0.05, so we reject the null hypothesis and 
#believe that the data has trend.

```

## Anlysis Seasonality
-seasonality
```{r}
#Differencing
print(ndiffs(sample_ts[,"Daily_offwind_gen"]))
print(nsdiffs(sample_ts[,"Daily_offwind_gen"]))

```


```{r}
#seasonsdj
sample_off_seasonadj <- sample_off_ts - sample_ts_off_decompose$seasonal
plot.ts(sample_off_seasonadj)
par(mfrow=c(1,2))
Acf(sample_off_seasonadj)
Pacf(sample_off_seasonadj)

##
#create dummy
dummy_off <- seasonaldummy(sample_ts[,2])
#fit linear model
seas_means_model_off <- lm(sample_ts[,2]~dummy_off)
#store regression coefficients
beta_int_off <- seas_means_model_off$coefficients[1]
beta_coeff_off <- seas_means_model_off$coefficients[2:52]
#compute seasonal component
nobsv <- nrow(sample_ts)
nobsv <- nobsv-1+1
offshore_seas_comp <- array(0,nobsv)
for (i in 1:nobsv){
  offshore_seas_comp[i] = (beta_int_off+beta_coeff_off%*%dummy_off[i,])
}
#Plot original data and seasonal component
ggplot(sample, aes(x=Time, y=sample$Daily_offwind_gen)) +
            geom_line(color="blue") +
            ylab("Wind Generation (MW)") +
            geom_line(aes(y=offshore_seas_comp), col="red")
#remove seasonal component
deaseason_offshore <- sample_off_ts - offshore_seas_comp
#plot original off shoredata and deaseasonal offshore data
ggplot(sample, aes(x=Time, y=sample$Daily_offwind_gen))+
            geom_line(color="blue")+
            ylab("Wind Generation (MW)")+
            geom_line(aes(y=deaseason_offshore), col="red")
```

## Tests
-stationary test
```{r}
#ADF
print(
  adf.test(sample_ts_off_deseason, alternative = "stationary")
)
#The P-value is 0.01, less than 0.05, so we reject the null hypothesis and
#believe that the data is stationary.
```



\newpage

# Model building
-Auto Correlation Function
-Partial Correlation Function
-Model Parameter Estimation
```{r}
#Sarima model
sample_off_sarima <- auto.arima(sample_ts[,"Daily_offwind_gen"])
print(sample_off_sarima)
checkresiduals(sample_off_sarima)

#Exponential smooth model and forecast(Terrible)
sample_off_es <- es(sample_ts[,"Daily_offwind_gen"],
                    model = "ZZZ",
                    silent = FALSE,
                    holdout = FALSE,
                    h = 39)
plot(sample_off_es)

#BSM model
sample_off_ss <- StructTS(sample_ts[,"Daily_offwind_gen"],
                          type = "BSM"
                          )
checkresiduals(sample_off_ss)
sample_off_ss_forecast <- forecast(sample_off_ss,h=39)
plot(sample_off_ss_forecast)

#STL + ETS
sample_ets_fit <- stlf(sample_msts,
                       h=39)
autoplot(full_ts[,2])+
  autolayer(sample_ets_fit, 
            series="STL+ETS",
            PI=FALSE)+
  ylab("Wind Generation(MW)")

#ARIMA + FOURIER
sample_arima_four <- auto.arima(sample_msts,
                                seasonal = FALSE,
                                lambda = 0,
                                xreg = fourier(sample_msts,
                                               K=12))

#TBATS
sample_tbats <- tbats(sample_msts)

```



\newpage

# Perform Forecast
-Forecast
-Model Accuracy
(use 2015-2019 to forecast 2020, use the accuracy to select the model)
-Model Selection
```{r}
#Sarima model
sample_off_sarima_forecast <- forecast(sample_off_sarima,
                                       h = 39)
plot(sample_off_sarima_forecast)

#ARIMA+Fourier
sample_off_arima_four_forecast <- forecast(sample_arima_four,
                                           xreg = fourier(sample_msts,
                                                          K=12,
                                                          h=39),
                                           h=39)
#TBATS
sample_off_tbats_forecast <- forecast(sample_tbats,
                                      h=39)

#plots
autoplot(full_ts[,"Daily_offwind_gen"])+
  autolayer(sample_off_sarima_forecast, PI = FALSE, series = "SARIMA")+
  autolayer(sample_off_ss_forecast, PI = FALSE, series = "BSM")+
  autolayer(sample_off_es$forecast, series = "SSES")+
  autolayer(sample_ets_fit, 
            series="STL+ETS",
            PI=FALSE)+
  autolayer(sample_off_arima_four_forecast,
            series = "ARIMA_Fourier",
            PI=FALSE)+
  autolayer(sample_off_tbats_forecast,
            series = "TBATS",
            PI=FALSE)+
  xlab("Year")+
  ylab("Generation(MW)")+
  coord_cartesian(xlim = c(2019,2021))

```
```{r}

#Accuracy
last_obs <- full_ts[262:300,"Daily_offwind_gen"]

sarima_score <- accuracy(sample_off_sarima_forecast$mean, last_obs)
sses_score <- accuracy(sample_off_es$forecast, last_obs)
bsm_score <- accuracy(sample_off_ss_forecast$mean, last_obs)
ets_score <- accuracy(sample_ets_fit$mean,last_obs)
arima_four_score <- accuracy(sample_off_arima_four_forecast$mean,last_obs)
tbats_score <- accuracy(sample_off_tbats_forecast$mean,last_obs)
score_table <-rbind.data.frame(sarima_score,
                               sses_score,
                               bsm_score,
                               ets_score,
                               arima_four_score,
                               tbats_score)

rownames(score_table) <- c("SARIMA","SSES","BSM","ETS","ARIMA_FOURIER","TBATS")
kbl(score_table, 
      caption = "Forecast Accuracy",
      digits = array(5,ncol(score_table))) %>%
  kable_styling(full_width = FALSE, position = "center") %>%
  kable_styling(latex_options="striped", stripe_index = which.min(score_table[,"MAPE"]))
```

\newpage

# Forecast Output
-forecast generation in 2021: forecast plots
```{r}
#MSTS
full_msts <- msts(full$Daily_offwind_gen,
                    seasonal.periods = c(52),
                    start = c(2015,01,01))


#STL + ETS
full2021_ets_fit <- stlf(full_msts,
                       h=52)
autoplot(full_ts[,2])+
  autolayer(full2021_ets_fit, 
            series="STL+ETS",
            PI=FALSE)+
  ylab("Wind Generation(MW)")

```

\newpage

# Forecast Limitation
-How to improve our model

