---
output: 
  pdf_document:
    keep_tex: yes
    fig_caption: yes
    number_sections: yes
geometry: margin=2.54cm
title: "Wind Energy Consumption/Production Trend Analysis and Forecast"
subtitle: "Time Series Analysis and Forecast"
author: "Chuqi Cai, Xueying Feng, Longyi Yang"
fontsize: 12pt
mainfont: Times New Roman
editor_options: 
  chunk_output_type: inline
---

\newpage
\tableofcontents 
\newpage
\listoftables 
\newpage
\listoffigures 
\newpage

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Set your working directory
#getwd()
setwd("~/Desktop/ENV 790 Time Series/ENV790_TSA_FinalProject")

# Load/install required packages
library(plyr) #Tools for Splitting, Applying and Combining Data
library(tidyverse) #Getting data frames to tidy
library(lubridate) #For dates and date-times
library(ggplot2)
library(forecast)  
library(Kendall)
library(tseries)
#library(outliers)
library(outliers)
library(smooth)
library(zoo)
library(kableExtra)

# Set your ggplot theme
mytheme <- theme_minimal(base_size = 12, base_family = "Times") + 
  theme(axis.text.x = element_text(color = "DarkGrey"),
        legend.position = "top") 
theme_set(mytheme)
```

# Rationale and Research Questions


\newpage

# Dataset Information
## Database Information
Introduce the source of our Data

## Data Content Information
Introduce the variable we are focusing on. Metadata from https://data.open-power-system-data.org/time_series/




\newpage

# Exploratory Analysis 
-wrangle data: sum up the generation per day. 
-initial plots (clean data if necessary, outliers, missing data)
-decompose
## Importing data
```{r warning = FALSE}
# Import dataset
Wind_Gen <- read.csv("./Data/DE_Wind_Generation_Data.csv")
str(Wind_Gen)

# Preparing data 
## Convert to date object
Wind_Gen$Time <- as.Date(Wind_Gen$utc_timestamp, format='%Y-%m-%d %H:%M:%OS')
str(Wind_Gen)


## Aggregate data into Daliy
# Wind_Gen_new <-  Wind_Gen%>%
#   group_by(Time) %>%
#   summarize(Daily_Wind_Gen = sum(wind_generation_actual, na.rm = TRUE),
#             Daily_OffWind_Gen = sum(wind_offshore_generation_actual, na.rm = TRUE),
#             Daily_Onwind_Gen = sum(wind_onshore_generation_actual, na.rm = TRUE))

## Aggregate data into monthly
# Wind_Gen_new <-  Wind_Gen%>%
#   group_by(Time=floor_date(Time, "month")) %>%
#   summarize(Monthly_Wind_Gen = sum(wind_generation_actual, na.rm = TRUE),
#             Monthly_OffWind_Gen = sum(wind_offshore_generation_actual, na.rm = TRUE),
#             Monthly_OnWind_Gen = sum(wind_onshore_generation_actual, na.rm = TRUE))

## Aggregate data into weekly
Wind_Gen_new <-  Wind_Gen %>%
  group_by(Time=floor_date(Time,unit="week",week_start = 4)) %>%
  summarize(Weekly_Wind_Gen = sum(wind_generation_actual, na.rm = TRUE),
            Weekly_Offwind_Gen = sum(wind_offshore_generation_actual, na.rm = TRUE),
            Weekly_OnWind_Gen = sum(wind_onshore_generation_actual, na.rm = TRUE))

str(Wind_Gen_new)

Wind_Gen_new <- as.data.frame(Wind_Gen_new)
str(Wind_Gen_new)
head(Wind_Gen_new)
tail(Wind_Gen_new)
```


## Transforming data into time series objects

```{r}
# Split time series data for training and test set
sample<-Wind_Gen_new[which(Wind_Gen_new$Time>="2015-01-01" & Wind_Gen_new$Time<="2019-12-31"),]
full<-Wind_Gen_new[which(Wind_Gen_new$Time>="2015-01-01" & Wind_Gen_new$Time<="2020-09-30"),]


# Convert to time series
# sample_ts<-ts(sample[,2:4], frequency = 365, start = c(2015,1,1), end = c(2020,01,01))
# full_ts<-ts(full[,2:4], frequency = 365, start = c(2015,1,1))

# sample_ts<-ts(sample[,2:4], frequency = 12, start = c(2015,1,1), end = c(2020,01,01))
# full_ts<-ts(full[,2:4], frequency = 12, start = c(2015,1,1))

sample_ts<-msts(sample[,2:4], seasonal.periods = c(52), start = c(2015,1,1), end = c(2020,01,01))
full_ts<-msts(full[,2:4], seasonal.periods = c(52), start = c(2015,1,1))

```


## Initial Plots

```{r message=FALSE, warning=FALSE}
#Plot 
ggplot(sample, aes(x=Time, y=Weekly_Wind_Gen)) +
  geom_line(color="blue") +
  ylab("Wind Generation (MW)") +
  geom_line(aes(y=Weekly_Offwind_Gen, col="Offshore Wind"))+
  geom_line(aes(y=Weekly_OnWind_Gen, col="Onshore Wind"))+
  theme(legend.position = "right") +
  scale_x_date(date_breaks = "1 years", date_labels = "%Y")+
  ylab("Wind Generation (MW)")+
  labs(colour="Energy Type")



```



## Onshore Wind data

```{r Onshore wind generation data}
#look at onshore data first
Onshore_sample_ts <- sample_ts[,3]
Onshore_full_ts <- full_ts[,3]

plot(Onshore_sample_ts, 
     xlab="Time", 
     ylab="Onshore Wind Generation (MW)",
     col="blue")

#ACF and PACF plots
par(mar=c(3,3,3,0));par(mfrow=c(1,2))
Acf(Onshore_sample_ts, lag = 100, plot = TRUE,main="ACF of Onshore wind")
Pacf(Onshore_sample_ts, lag = 100, plot = TRUE,main="PACF of Onshore wind")
```


## Onshore Wind data (log)

```{r message=FALSE, warning=FALSE}
#A multiplicative time series can be converted to additive by taking a log of the time series.
#log  data
Onshore_sample_logts <- log (Onshore_sample_ts)
Onshore_full_logts <- log (Onshore_full_ts) 


# Create new logged sample data frame
TimeSample <- as.Date(sample$Time)
OnshoreSample_log <- cbind.data.frame(TimeSample, Onshore_sample_logts)
str(OnshoreSample_log)
class(OnshoreSample_log)
head(OnshoreSample_log)


# Create new logged full data frame
TimeFull <- as.Date(full$Time)
OnshoreFull_log <- cbind.data.frame(TimeFull, Onshore_full_logts)
str(OnshoreFull_log)
class(OnshoreFull_log)
head(OnshoreFull_log)

#Plot log onshore wind data
ggplot(OnshoreSample_log, aes(x=TimeSample, y=Onshore_sample_logts)) +
  geom_line(color="blue") +
  ylab("Logged Onshore Wind Generation") +
  geom_smooth(color="red",method="lm") 
```

\newpage

# Analysis

## Decomposing time series objects

```{r Decompose}
#The decompose() splits the time series into seasonality, trend and error components.
#Identify if a timeseries is additive or multiplicative: IF the variance in the graph is constant through out from central line then its additive else multiplicative.

#Additive model is used when the variance of the time series doesn't change over different values of the time series.
#On the other hand, if the variance is higher when the time series is higher then it often means we should use a multiplicative models.

#In this case, the size of the seasonal and random fluctuations change over time and the level of the time series, it is a multiplicative time series.

Onshore_sample_logts_decompose <- decompose(Onshore_sample_logts,type = "additive")
plot(Onshore_sample_logts_decompose,yax.flip = TRUE)

##The trend component is an increasing pattern. The random component is kind of randomness, so there still are some seasonality on that.
```

## Run stationarity and derterministic test

```{r ADF and Mann Kendall}
#Run ADF
#Start by running ADF to check for unit root. Unit root is related to stochastic trend
# H0: data has unit root
# H1: data is stationary

print("Results for ADF test:")
print((adf.test(Onshore_sample_logts,alternative="stationary")))
#Note that p-value greater then 0.05, so we accept H0, meaning the series does  have a stochastic trend (H0).
#Next step is to difference the series to remove the trend.
#Difference the data at lag 1


#Run Mann Kendall
#There is seasonality in data, so use "SeasonalMannKendall"
# H0: There is no trend present in the data (stationary)
# H1: A trend is present in the data

print("Results for Mann Kendall:") 
print(summary(SeasonalMannKendall(Onshore_sample_logts)))
#p-value less < 0.05, we reject null hypothesis. time and onshore wind generation have significant positive correlation, and data has a derterministic trend.



```

## Trends Anlysis

```{r Diff()}
#first-differencing a time series will remove a linear trend (i.e., differences = 1); 
#twice-differencing will remove a quadratic trend (i.e., differences = 2). 
#In addition, first-differencing a time series at a lag equal to the period will remove a seasonal trend

print(ndiffs(Onshore_sample_logts)) # number for differencing needed
Onshore_sample_logts_diff <- diff(Onshore_sample_logts, differences = 1)   

#plot
plot(Onshore_sample_logts_diff)


#ACF and PACF plots
par(mar=c(3,3,3,0));par(mfrow=c(1,2))
Acf(Onshore_sample_logts_diff, lag = 100, plot = TRUE,main="ACF of Onshore wind")
Pacf(Onshore_sample_logts_diff, lag = 100, plot = TRUE,main="PACF of Onshore wind")
```


## Seasonality Anlysis

```{r seasadj(), message=FALSE, warning=FALSE}
# number for seasonal differencing needed
print(nsdiffs(Onshore_sample_logts))

stl_Onshore_sample_logts <- stl(Onshore_sample_logts,"periodic")  # decompose the TS
deseasonal_Onshore_sample_logts <- seasadj(stl_Onshore_sample_logts)  # de-seasonalize

#Plot series
plot(deseasonal_Onshore_sample_logts, col ="blue")

ggplot(OnshoreSample_log, aes(x=TimeSample, y=Onshore_sample_logts)) +
  geom_line(color="orange") +
  ylab("Logged Wind Generation (MW)") +
  #geom_smooth(color="red",method="lm") +
  geom_line(aes(y=deseasonal_Onshore_sample_logts), col="blue")+
  geom_smooth(aes(y=deseasonal_Onshore_sample_logts),color="purple",method="lm") 


#ACF and PACF plots
par(mfrow=c(1,2))
Acf(deseasonal_Onshore_sample_logts, lag = 100, plot = TRUE,,main="")
Pacf(deseasonal_Onshore_sample_logts, lag = 100, plot = TRUE,main="")

```


\newpage

# Perform Forecast
## Fitting Models to the original (seasonal) series

```{r Create variables}
# This is helpful whenever you need to change forecasting horizon you only need to change it here
n_for <- 40 #play with this, change to 12, 23, 2 and check of the best model is still the same

Sample_obs <- nrow(OnshoreSample_log)
#last_obs
OnshoreSampleLast_obs <- Onshore_sample_logts[(Sample_obs-n_for+1):Sample_obs]

Full_obs <- nrow(OnshoreFull_log)
#last_obs
OnshoreFullLast_obs <- Onshore_full_logts[(Full_obs-n_for+1):Full_obs] 

```

### Model 1: Arithmetic mean

```{r message=FALSE, warning=FALSE}
OnshoreLog_MEAN_seas <- meanf(y = Onshore_sample_logts, h = n_for)
checkresiduals(OnshoreLog_MEAN_seas)
plot(OnshoreLog_MEAN_seas)  #plot forecasts
```
Note a clear trend on residuals series, showing that the mean is not a good to model the trend component. And aside from trend the seasonal component is also not being modeled.


### Model 2: Seasonal naive

```{r message=FALSE, warning=FALSE}
OnshoreLog_SNAIVE_seas <- snaive(Onshore_sample_logts, h=n_for)
checkresiduals(OnshoreLog_SNAIVE_seas)
plot(OnshoreLog_SNAIVE_seas)

```
The residuals for the seasonal naive don't seem to have a strong trend. Because it repeats the observations that happen in a previous seasonal lag (in this case one year ago), the seasonal naive is able to model the trend and seasonal component. ACF shows no significant self correlation.


### Model 3: ARIMA

```{r Put the seasonality back on your forecasted values, message=FALSE, warning=FALSE}

deseasonal_OnshoreLog_autofit <- auto.arima(deseasonal_Onshore_sample_logts)
checkresiduals(deseasonal_OnshoreLog_autofit)

deseasonal_OnshoreLog_ARIMA_for <- forecast(deseasonal_OnshoreLog_autofit, h=n_for)
plot(deseasonal_OnshoreLog_ARIMA_for)

#Seasonal component from your decompose object 
OnshoreLog_seas<-Onshore_sample_logts_decompose$seasonal


#check last year data
OnshoreLog_seas[(Sample_obs-n_for+1):Sample_obs]


OnshoreLog_ARIMA_for <-deseasonal_OnshoreLog_ARIMA_for$mean+OnshoreLog_seas[(Sample_obs-n_for+1):Sample_obs]

plot(OnshoreLog_ARIMA_for)

#Make plot
par(mar=c(2,4,1,0))
plot(Onshore_full_logts, type="l", xlab="Year",ylab="Logged Onshore Wind Generation")
lines(OnshoreLog_ARIMA_for, col="red")
legend("topright", 
  legend=c("original seasonal data(2015-2020)","forecast data with seasonality (2020)"), 
  col = c("black", "red"),
  lty=1:1, 
  cex=0.5)

```


### Model 4: SARIMA

```{r message=FALSE, warning=FALSE}
# SARIMA is seasonal ARIMA and it is used with time series with seasonality.
OnshoreLog_SARIMA_autofit <- auto.arima(Onshore_sample_logts)
checkresiduals(OnshoreLog_SARIMA_autofit)

OnshoreLog_SARIMA_for <- forecast(OnshoreLog_SARIMA_autofit,h=n_for)
plot(OnshoreLog_SARIMA_for)
```
The residual series seems to be random and ACF shows no significant self correlation, but forecast plot seems not very well.


## Fitting State Space Models to the original (seasonal) series
### Model 5: SS Exponential smoothing

```{r SSES, message=FALSE, warning=FALSE}
# Exponential smoothing under the state space model
# ES can be used to represent trend and seasonal
OnshoreLog_SSES_seas <- es(Onshore_sample_logts,model="MAM",h=n_for,holdout=FALSE, silent = "output")
plot(OnshoreLog_SSES_seas)
checkresiduals(OnshoreLog_SSES_seas)
```
The best model here was a ETS(MAM) which means we are fitting an multiplicative random error, an additive trend and a multiplicative seasonal component.


### Model 6: SS with StructTS()

```{r BSM, message=FALSE, warning=FALSE}
#type = "BSM", is a local trend model with an additional seasonal component.
OnshoreLog_SS_seas <- StructTS(Onshore_sample_logts, type = "BSM") #seasonality: BSM
checkresiduals(OnshoreLog_SS_seas)

#Generating forecasts
# StructTS() does not call the forecast() internally so we need one more step
OnshoreLog_SS_for <- forecast(OnshoreLog_SS_seas,h=n_for)
plot(OnshoreLog_SS_for)
```
Forecast plot is not very well.


## Fitting Complex Seasonality models to the original (seasonal) series
### Model 7: STL + ETS

```{r STL + ETS, message=FALSE, warning=FALSE}
#Fit and forecast STL + ETS model to data
OnshoreLog_ETS_fit <-  stlf(Onshore_sample_logts,h=n_for)

#Plot foresting results
autoplot(OnshoreLog_ETS_fit) + ylab("Logged Onshore Wind Generation")

#Plot model + observed data
autoplot(Onshore_full_logts) +
  autolayer(OnshoreLog_ETS_fit, series="STL + ETS",PI=FALSE) +
  ylab("Logged Onshore Wind Generation")
```

### Model 8: ARIMA + FOURIER terms
Since we have multiple seasonalities, the SARIMA model will not work. But we can work with an ARIMA model with Fourier terms for each seasonal period.

```{r ARIMA + FOURIER, message=FALSE, warning=FALSE}
 
#Fit arima model with fourier terms as exogenous regressors
# seasonal = FALSE is the same as P=D=Q=0
OnshoreLog_ARIMA_Four_fit <- auto.arima(Onshore_sample_logts, 
                             seasonal=FALSE, 
                             lambda=0,
                             xreg=fourier(Onshore_sample_logts, 
                                          K=12) 
                             )

#Forecast with ARIMA fit
#also need to specify h for fourier terms
OnshoreLog_ARIMA_Four_for <- forecast(OnshoreLog_ARIMA_Four_fit,
                           xreg=fourier(Onshore_sample_logts,
                                        K=12,
                                        h=n_for),
                           h=n_for) 

#Plot foresting results
autoplot(OnshoreLog_ARIMA_Four_for) + ylab("Logged Onshore Wind Generation")

#Plot model + observed data
autoplot(Onshore_full_logts) +
  autolayer(OnshoreLog_ARIMA_Four_for, series="ARIMA_FOURIER",PI=FALSE) +
  ylab("Logged Onshore Wind Generation")
```

### Model 9: TBATS

```{r TBATS, message=FALSE, warning=FALSE}
# TBATS is a trigonometric seasonal variation of BATS
OnshoreLog_TBATS_fit <- tbats(Onshore_sample_logts)

OnshoreLog_TBATS_for <- forecast(OnshoreLog_TBATS_fit, h=n_for)

#Plot foresting results
autoplot(OnshoreLog_TBATS_for) +
  ylab("Logged Onshore Wind Generation") 

#Plot model + observed data
autoplot(Onshore_full_logts) +
  autolayer(OnshoreLog_TBATS_for, series="TBATS",PI=FALSE)+
  ylab("Logged Onshore Wind Generation") 
```

### Plotting All Fitted Models

```{r All plot, message=FALSE, warning=FALSE}
autoplot(Onshore_full_logts) +
  autolayer(OnshoreLog_MEAN_seas, PI=FALSE, series="Arithmetic mean") +
  autolayer(OnshoreLog_SNAIVE_seas, PI=FALSE, series="Seasonal Naive") +
  autolayer(OnshoreLog_ARIMA_for, PI=FALSE, series="ARIMA") +
  autolayer(OnshoreLog_SARIMA_for, PI=FALSE, series="SARIMA") +
  autolayer(OnshoreLog_SSES_seas$forecast, series="SSES") +
  autolayer(OnshoreLog_SS_for,PI=FALSE,series="BSM") + 
  autolayer(OnshoreLog_ETS_fit, PI=FALSE, series="STL+ETS") +
  autolayer(OnshoreLog_ARIMA_Four_for, PI=FALSE, series="ARIMA + Fourier") +
  autolayer(OnshoreLog_TBATS_for,PI=FALSE, series="TBATS") +
  xlab("Year") + 
  ylab("Logged Onshore Wind Generation") +
  guides(colour=guide_legend(title="Forecast"))
```

```{r last two years plots, message=FALSE, warning=FALSE}
autoplot(window(Onshore_full_logts,start=2019)) +
  #autolayer(OnshoreLog_MEAN_seas, PI=FALSE, series="Arithmetic mean") +
  autolayer(OnshoreLog_SNAIVE_seas, PI=FALSE, series="Seasonal Naive") +
  autolayer(OnshoreLog_ARIMA_for, PI=FALSE, series="ARIMA") +
  #autolayer(OnshoreLog_SARIMA_for, PI=FALSE, series="SARIMA") +
  autolayer(OnshoreLog_SSES_seas$forecast, series="SSES") +
  #autolayer(OnshoreLog_SS_for,PI=FALSE,series="BSM") + 
  autolayer(OnshoreLog_ETS_fit, PI=FALSE, series="STL+ETS") +
  autolayer(OnshoreLog_ARIMA_Four_for, PI=FALSE, series="ARIMA + Fourier") +
  autolayer(OnshoreLog_TBATS_for,PI=FALSE, series="TBATS") +
  xlab("Year") + 
  ylab("Logged Onshore Wind Generation") +
  guides(colour=guide_legend(title="Forecast"))
```

### Model Accuracy
(use 2015-2019 to forecast 2020, use the accuracy to select the model)

```{r Accuracy Scores}
#Model 1: Arithmetic mean
#OnshoreLog_MEAN_scores <- accuracy(OnshoreLog_MEAN_seas)  #store the performance metrics

#Model 2: Seasonal naive 
OnshoreLog_SNAIVE_scores <- accuracy(OnshoreLog_SNAIVE_seas, OnshoreFullLast_obs)
OnshoreLog_SNAIVETest_scores <- OnshoreLog_SNAIVE_scores[2]

# Model 3: ARIMA
OnshoreLog_ARIMA_for_scores <- accuracy(OnshoreLog_ARIMA_for,OnshoreFullLast_obs)  #store the performance metrics

# Model 4: SARIMA
#OnshoreLog_SARIMA_scores <- accuracy(OnshoreLog_SARIMA_fore$mean,OnshoreFullLast_obs)

# Model 3:  SSES
OnshoreLog_SSES_scores <- accuracy(OnshoreLog_SSES_seas$forecast,OnshoreFullLast_obs)

# Model 6:  BSM 
#OnshoreLog_SS_scores <- accuracy(OnshoreLog_SS_forecast$mean,OnshoreFullLast_obs)

#Model 7: STL + ETS
OnshoreLog_ETS_scores <- accuracy(OnshoreLog_ETS_fit$mean,OnshoreFullLast_obs)  

#Model 8: ARIMA + Fourier 
OnshoreLog_ARIMA_Four_scores <- accuracy(OnshoreLog_ARIMA_Four_for$mean,OnshoreFullLast_obs)

# Model 9:  TBATS 
OnshoreLog_TBATS_scores <- accuracy(OnshoreLog_TBATS_for$mean,OnshoreFullLast_obs)


#create data frame
Onshore_scores <- as.data.frame(
  rbind(OnshoreLog_SNAIVETest_scores, OnshoreLog_ARIMA_for_scores, OnshoreLog_SSES_scores, 
        OnshoreLog_ETS_scores, OnshoreLog_ARIMA_Four_scores, OnshoreLog_TBATS_scores))
row.names(Onshore_scores) <- c("SNAIVE","ARIMA","SSES","STL+ETS","ARIMA+Fourier","TBATS")

#choose model with lowest MPE/RMSE
best_model_index <- which.min(Onshore_scores[,"MPE"])
cat("The best model by MPE is:", row.names(Onshore_scores[best_model_index,]))
```


```{r Model Accuracy Table, echo=FALSE, message=FALSE, warning=FALSE}
library(kableExtra)
kbl(Onshore_scores,
    caption = "Forecast Accuracy for Data",
    digits = array(7,ncol(Onshore_scores))) %>%
  kable_styling(full_width = FALSE, position = "center") %>%
  #highlight model with lowest MPE
  #kable_styling(latex_options="striped", stripe_index = which.min(Onshore_scores[,"MPE"]))
  row_spec(best_model_index, bold=T, color="black", background = "yellow")
```

-Model Selection

\newpage

# Forecast Onshore Wind Generation in 2021

```{r Forecast 2021 varible}
n_week <- Full_obs-Sample_obs+1+52

```


```{r SSES 2021 forcast, message=FALSE, warning=FALSE}
# Exponential smoothing under the state space model
# ES can be used to represent trend and seasonal
OnshoreLog_SSES_2021 <- es(Onshore_full_logts,model="MAM",h=n_week,holdout=FALSE, silent = "output")
plot(OnshoreLog_SSES_2021)
checkresiduals(OnshoreLog_SSES_2021)
```


```{r message=FALSE, warning=FALSE}
OnshoreLog_SNAIVE_2021 <- snaive(Onshore_full_logts, h=n_week)
checkresiduals(OnshoreLog_SNAIVE_2021)
plot(OnshoreLog_SNAIVE_2021)

```


```{r STL + ETS 2021 forcast, message=FALSE, warning=FALSE}
#Fit and forecast STL + ETS model to data
OnshoreLog_ETS_fit2021 <-  stlf(Onshore_full_logts,h=n_week)

#Plot foresting results
autoplot(OnshoreLog_ETS_fit2021) + ylab("Logged Onshore Wind Generation")


```


\newpage

# Forecast Limitation
-How to improve our model

